Reproducibility in plant pathology: where do we stand and a way forward

### 2021-06-22 analysis/paper/paper.Rmd
remove unecessary spaces
Replace "donors" with "funding agencies"

Recently, open science has been highlighted with many donors expecting data to be available [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists interested in sharing and collaborating more widely [@Wald2010].

>>>>

Recently, open science has been highlighted with many funding agencies expecting data to be available upon the conclusion of the research project [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists interested in sharing and collaborating more widely [@Wald2010].
